VarSight: Prioritizing Clinically Reported Variants with Binary Classification Algorithms

### 2019-01-15 paper/data_template.tex
data_template will at least build a file for path only, just not formatted correctly later

\multirow{2}{*}{Classifier}&\multicolumn{4}{c||}{Performance}&\multicolumn{4}{c}{Rank Median(Mean)} \\ \cline{2-9}
&TPR&FPR&AUC&CV10 Acc.&Overall (n={{ TEST_COUNTS.OVERALL }})&
VUS (n={{ TEST_COUNTS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE }})&
Likely Path. (n={{ TEST_COUNTS.LIKELY_PATHOGENIC }})&Pathogenic (n={{ TEST_COUNTS.PATHOGENIC }}) \\ \hline
{% for clf_label in CLF_LABELS %}
    {{ clf_label }}&
    {{ '%0.2f' % CLASSIFIERS[clf_label].TEST_TPR_RATE }}&
    {{ '%0.2f' % CLASSIFIERS[clf_label].TEST_FPR_RATE }}&
    {{ '%0.2f' % CLASSIFIERS[clf_label].ROC_AUC }}&
    {{ '%0.2f+-%0.2f' % (CLASSIFIERS[clf_label].CV10_BALANCED_ACCURACY[0], CLASSIFIERS[clf_label].CV10_BALANCED_ACCURACY[1]) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.OVERALL), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.OVERALL)) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE)) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.LIKELY_PATHOGENIC), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.LIKELY_PATHOGENIC)) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.PATHOGENIC), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.PATHOGENIC)) }} \\
{% endfor %}

>>>>

\multirow{2}{*}{Ranking System}&\multicolumn{4}{c||}{Case Rank - Median (Mean)}&\multicolumn{4}{c}{Percentage in Top X Variants - X=(1, 10, 20)} \\ \cline{2-9}
&All (n={{ TEST_COUNTS.OVERALL }})&
VUS (n={{ TEST_COUNTS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE }})&
LP (n={{ TEST_COUNTS.LIKELY_PATHOGENIC }})&Path. (n={{ TEST_COUNTS.PATHOGENIC }})&
All (n={{ TEST_COUNTS.OVERALL }})&
VUS (n={{ TEST_COUNTS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE }})&
LP (n={{ TEST_COUNTS.LIKELY_PATHOGENIC }})&Path. (n={{ TEST_COUNTS.PATHOGENIC }}) \\ \hhline{=|=|=|=|=||=|=|=|=}
{% for cs_label in CS_LABELS %}
    {{ cs_label }}&
    {% for LEVEL in LEVELS %}
        {{ '%0.1f (%0.2f)' % (np.median(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]), np.mean(COMPARISON[cs_label].TEST_RANKINGS[LEVEL])) }}&
    {% endfor %}
    {% for LEVEL in LEVELS %}
        {{ '%d, %d, %d' % 
            (100.0*np.sum(np.array(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]) <= 1) / len(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]),
            100.0*np.sum(np.array(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]) <= 10) / len(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]),
            100.0*np.sum(np.array(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]) <= 20) / len(COMPARISON[cs_label].TEST_RANKINGS[LEVEL]))
        }}
        {% if LEVEL != 'PATHOGENIC' %}
            &
        {% endif %}
    {% endfor %}
    \\
{% endfor %}
\hhline{=|=|=|=|=||=|=|=|=}

Exomiser$^*$&
{% for LEVEL in LEVELS %}
    {{ '%0.1f (%0.2f)' % (np.median(EXOMISER.TEST_RANKINGS[LEVEL]), np.mean(EXOMISER.TEST_RANKINGS[LEVEL])) }}&
{% endfor %}
{% for LEVEL in LEVELS %}
    {{ '%d, %d, %d' % 
        (100.0*np.sum(np.array(EXOMISER.TEST_RANKINGS[LEVEL]) <= 1) / len(EXOMISER.TEST_RANKINGS[LEVEL]),
        100.0*np.sum(np.array(EXOMISER.TEST_RANKINGS[LEVEL]) <= 10) / len(EXOMISER.TEST_RANKINGS[LEVEL]),
        100.0*np.sum(np.array(EXOMISER.TEST_RANKINGS[LEVEL]) <= 20) / len(EXOMISER.TEST_RANKINGS[LEVEL]))
    }}
    {% if LEVEL != 'PATHOGENIC' %}
        &
    {% endif %}
{% endfor %}
\\ \hhline{=|=|=|=|=||=|=|=|=}

{% for clf_label in CLF_LABELS %}
    {{ clf_label }}&
    {% for LEVEL in LEVELS %}
        {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL])) }}&
    {% endfor %}
    {% for LEVEL in LEVELS %}
        {{ '%d, %d, %d' % 
            (100.0*np.sum(np.array(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]) <= 1) / len(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]),
            100.0*np.sum(np.array(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]) <= 10) / len(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]),
            100.0*np.sum(np.array(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]) <= 20) / len(CLASSIFIERS[clf_label].TEST_RANKINGS[LEVEL]))
        }}
        {% if LEVEL != 'PATHOGENIC' %}
            &
        {% endif %}
    {% endfor %}
    \\
{% endfor %}
